### 2008-12-05 doc/sec/Sec_paper.tex
little changes in sec doc

\liststyleLiii
\begin{itemize}
\item \textit{Integration of community authentication} -{}-{}- to
utilize the standardized community authentication from Shibboleth
Identity Provider software when users authenticate against Grid
services.
\item \textit{Short lived credential service} \ {}-{}-{}- to issue the
short lived X.509 certificate for user by using the community
authentication, in order to interoperate with services that depends on
PKI based mutual authentication.
\item \textit{Credential delegation service} -{}-{}- to process the
X.509 credential delegation as a normal Web Service, in order to
provide single sign-on characteristic.
\item \textit{Message level authentication} -{}-{}- to provide message
level authentication by implementing WS-Security.
\item 
\bigskip
\end{itemize}

@@

\liststyleLv
\begin{enumerate}
\item The communication between delegation client and service is based
on mutual authentication between proxy certificate and service
certificate, instead, it is based on mutual authentication between
service certificate and service certificate.
\item The delegation service will not generate any certificate request,
instead, it picks the public key from its own service certificate, and
sends back to delegation client.
\end{enumerate}
Figure 6 shows the token change due to delegation. On the left side, B
is the identity of the attesting entity{\textquotesingle}s X509 token
mentioned above, while A is the identity of issuing authority, and the
SOAP message is signed by B{\textquotesingle}s private key. On the
right side, C is the identity of the delegation service, ans now the
SOAP message is signed by C{\textquotesingle}s private key.

@@

\begin{center}
\includegraphics[width=4.2571in,height=2.152in]{Secpaper-img6.png}
\end{center}
{\centering
\ \ \ \ \ \ \ \ \ Figure 6. Token before and after delegation
\par}

>>>>

\liststyleLiii
\begin{itemize}
\item \textit{Integration of community authentication} -{}-{}- to
utilize the standardized community authentication from Shibboleth
Identity Provider software when users authenticate against Grid
services.
\item \textit{Short lived credential service} \ {}-{}-{}- to issue the
short lived X.509 certificate for user by using the community
authentication, in order to interoperate with services that depends on
PKI based mutual authentication.
\item \textit{Credential delegation service} -{}-{}- to process the
X.509 credential delegation as a normal Web Service, in order to
provide single sign-on characteristic.
\item \textit{Message level authentication} -{}-{}- to provide message
level authentication by implementing WS-Security.
\item \textit{SAML token delegation service} -{}-{}- to process the WS
Security SAML token in order to provide single sign-on for SOAP message
level authentication
\end{itemize}

@@

\liststyleLv
\begin{enumerate}
\item The communication between delegation client and service is based
on mutual authentication between proxy certificate and service
certificate, instead, it is based on mutual authentication between
service certificate and service certificate.
\item The delegation service will not generate any certificate request,
instead, it picks the public key from its own service certificate, and
sends back to delegation client.
\end{enumerate}
Figure 6 shows the SOAP message header is changed due to delegation. On
the left side, B is the identity of the attesting
entity{\textquotesingle}s X509 token mentioned above, while A is the
identity of issuing authority, and the SOAP message is signed by
B{\textquotesingle}s private key. On the right side, C is the identity
of the delegation service (also C is the identity of the target service
\ to which the B will access), and now the SOAP message is signed by
C{\textquotesingle}s private key.

@@

\begin{center}
\includegraphics[width=4.2571in,height=2.152in]{Secpaper-img6.png}
\end{center}
{\centering
\ \ \ \ \ \ \ \ \ Figure 6. SOAP message header with SAML delegation
token inside
\par}
